---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dotnet

<!-- badges: start -->
<!-- badges: end -->

The primary goal of {dotnet} is to provide a [{knitr}](https://yihui.org/knitr/) [engine](https://yihui.org/knitr/demo/engines/) for the [C#](https://docs.microsoft.com/en-us/dotnet/csharp/) and [F#](https://docs.microsoft.com/en-us/dotnet/fsharp/) languages and the [.NET Framework](https://dotnet.microsoft.com/). Internally, it accomplishes via an R6-based interface for the `dotnet` command line interface for building .NET applications. See `?DotNetApp` for details.

*Not to be confused* with:

- [{rDotNet}](https://cran.r-project.org/package=rDotNet) R package which is a "low-level interface to '.NET' virtual machine" and which "can create '.NET' objects, call methods, get or set properties, call static functions, etc."
- [R.NET](https://rdotnet.github.io/rdotnet/) NuGet package which "enables the .NET Framework to interoperate with the R statistical language in the same process"

**Notice**: this package is released as-is. I don't know that I'll be able to maintain it all that much. Like, the original motivation for this package was wanting to write a blog post about Bayesian inference and probabilistic programming with [Infer.NET](https://dotnet.github.io/infer/) in [R Markdown](https://rmarkdown.rstudio.com/) for my [{blogdown}](https://bookdown.org/yihui/blogdown/)-based site. Which is to say it was a fun, goofy exercise in learning how to make a custom knitr engine. Also, "C#/F# in R Markdown in blogdown-based websites" is a VERY obscure use-case. Let me know on Twitter if you use this package. (I'm [bearloga](https://twitter.com/bearloga) on there.)

It is licensed under [BSD 2-Clause "Simplified" License](LICENSE.md).

## Installation

To start rendering R Markdown documents with `dotnet` engine chunks, you need to be able to build .NET apps on your system. Download and install the [.NET SDK](https://dotnet.microsoft.com/download). If you can run `dotnet` in Terminal without problems, you're set.

``` r
remotes::install_github("bearloga/dotnet")
```

## Usage

First, the `dotnet` engine must be registered with knitr:

```{r}
dotnet::register_engine()
```

Once registered with knitr, we use the `dotnet` engine to run programs written in C#:

````
`r ''````{dotnet}
using System;
```
````

The following examples are `dotnet`-using chunks in this README's source Rmd document.

```{dotnet hello_world_cs, cache=TRUE}
using System;
class Program {
  static void Main(string[] args) {
    Console.WriteLine("Hello from C# and R Markdown!");
  }
}
```

...and programs written in F#, by specifying `engine.opts = list(language = 'F#')` in the chunk options:

```{dotnet hello_world_fs, engine.opts = list(language = 'F#'), cache=TRUE}
open System
[<EntryPoint>]
let main argv =
    printfn "Hello from F# and R Markdown!"
    0 // return an integer exit code
```

Programs with source code split across multiple chunks are supported. Refer to the [multi-chunk programs vignette](vignettes/multi-chunk-program.Rmd) for reference.

Programs with dependencies on NuGet packages can add those via `engine.opts`. For example:

````
`r ''````{dotnet, engine.opts = list(add_packages = c('Microsoft.ML.Probabilistic.Compiler'))}
using System;
using Microsoft.ML.Probabilistic.Models;
```
````

This is demonstrated in the ["Inference on two coins with Infer.NET" vignette](vignettes/two-coins.Rmd).

Refer to `?register_engine` for more information about the `dotnet` knitr engine..