\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={RYO®, ENG LIAN HU},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}
\DeclareUnicodeCharacter{00A0}{ }

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{RYO®, ENG LIAN HU}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}


% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{2}
\tableofcontents
}
\subsection{Curriculum Vitae}\label{curriculum-vitae}

\(®γθ\), Eng Lian Hu

\subsubsection{About Me}\label{about-me}

\begin{longtable}[c]{@{}lr@{}}
\toprule
\textbf{Title} & \textbf{Details}\tabularnewline
\midrule
\endhead
Date of Birth & 1984-10-22\tabularnewline
Age & 30y 11m 24d\tabularnewline
Malaysian Phone Number &
\href{tel:+60172100905}{+6-017-2100905}\tabularnewline
Taiwanese Phone Numner &
\href{tel:+8860989104576}{+886-098-910-4576}\tabularnewline
Home Landline Contact &
\href{tel:+60389570938}{+6-03-89570938}\tabularnewline
Email Address &
\href{mailto:englianhu@gmail.com}{\nolinkurl{englianhu@gmail.com}}\tabularnewline
Current Address & 43300 Seri Kembangan, Selangor,
Malaysia\tabularnewline
Home Town & 45500 Tanjong Karang, Selangor, Malaysia\tabularnewline
Nationality & Malaysian\tabularnewline
Religion & Buddha\tabularnewline
\bottomrule
\end{longtable}

\subsubsection{Education}\label{education}

\begin{description}
\item[Apr-2014 to May-2016 (expected)]
\textbf{Professional Certificate, Specialization Data Science};
\href{http://www.coursera.org}{Cousera} -
\href{https://www.jhu.edu/}{Johns Hopkins University (JHU)}

\begin{itemize}
\tightlist
\item
  \emph{01 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/AjMdkzyHyA2JWRRL}{The
  Data Scientist's Toolbox}}
\item
  \emph{02 Course title :
  \href{https://www.coursera.org/account/accomplishments/certificate/VBB2XUA29B}{R
  Programming}}
\item
  \emph{03 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/Q5HBLbpBekrW43Jd}{Getting
  and Cleaning Data}}
\item
  \emph{04 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/4Gz8BmPsnuknW93A}{Exploratory
  Data Analysis}}
\item
  \emph{05 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/xpNfvxWs8uMMYrjs}{Reproducible
  Research}}
\item
  \emph{06 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/jXzs4bAFXZfJ3Dne}{Statistical
  Inference}}
\item
  \emph{07 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/Su7PgrMXVGYrU4cM}{Regression
  Models}}
\item
  \emph{08 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/j6DpQhLYeRj54dvS}{Practical
  Machine Learning}}
\item
  \emph{09 Course title :
  \href{https://www.coursera.org/account/accomplishments/records/ERvuyAZm6CG45EUS}{Developing
  Data Products}}
\item
  \emph{10 Course title : \href{}{Data Science Capstone}}
\end{itemize}
\item[Jun-2015 to Aug-2015]
\textbf{Professional Certificate, Specialization Data Science};
\href{http://www.coursera.org}{Cousera} -
\href{https://www.umich.edu/}{University of Michigan (UM)}

\begin{itemize}
\tightlist
\item
  \emph{Course title :
  \href{https://www.coursera.org/account/accomplishments/records/GA4cGW59ETHAevCa}{Programming
  for Everybody (Python)}}
\end{itemize}
\end{description}

\subsubsection{Experience}\label{experience}

\begin{description}
\item[May-2015 to Sep-2015]
\textbf{Online Gaming, Customer Service}; OneMedia Sdn Bhd

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR2500}
\item
  \emph{Job Task : Handling inbound and outbound calls, livechat,
  feedback, all deposit and withdrawal transactions.}
\item
  \emph{Resson of Leaving : Superior request change to commission based
  sales and marketing but not my strength, therefore choose resign.}
\end{itemize}
\item[Feb-2015 to Apr-2015]
\textbf{Online Retails, Fraud Prevention};
\href{http://www.apple.com}{Apple Inc.}

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR4000}
\item
  \emph{Job Task : Handling inbound and outbound calls, check and
  approve/reject customers' ordered transactions.}
\item
  \emph{Resson of Leaving : Superior request to hit certain quantity of
  filtering transactions, therefore choose resign.}
\end{itemize}
\item[Nov-2013 to Apr-2014]
\textbf{Online Gaming Trading, Team Leader/Trader};
\href{http://www.gb-links.com/}{SBSolutionCorp Ltd}

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR3800}
\item
  \emph{Job Task : Handling few members to update scores and bets
  settlement.}
\item
  \emph{Resson of Leaving : Superior request hire more team members to
  lease the job, but I just would like to enjoy simple life office
  worker, therefore choose resign.}
\end{itemize}
\item[Nov-2012 to May-2013]
\textbf{TV Broadcasting Channel, Video Editor};
\href{http://www.udrive-media.com/}{U-Drive Media Sdn Bhd}

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR2450}
\item
  \emph{Job Task : Watching and filtering video streaming from abroad
  prior to play in our country.}
\item
  \emph{Resson of Leaving : Director request change to account or
  marketing department, but marketing is not my strength and I just
  would like to enjoy simple life office worker, therefore choose
  resign.}
\end{itemize}
\item[Mar-2008 to Jul-2012]
\textbf{Outsourcing Business, Customer Service};
\href{http://www.scicom-intl.com/}{Scicom (MSC) Bhd}

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR3656.25}
\item
  \emph{Job Task : Handling inbound and outbound calls, livechat,
  feedback, all deposit, withdrawal and also phone bets' transactions.
  Sometimes need to do translation and also analysis job tasks}
\item
  \emph{Resson of Leaving : HR request change project since closed
  project, since there has no sportsbook related project besides
  Ladbrokes during that time therefore choose resign.}
\end{itemize}
\item[Jul-2006 to Jun-2007]
\textbf{Online Gambling, Trainer/Trader}; Caspo Inc.

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR5919.27}
\item
  \emph{Job Task : Provides training to newbies on sportsbook trading
  and live scout. Need to backup for trading as well. Sometimes need to
  do translation and also analysis job tasks.}
\item
  \emph{Resson of Leaving : Cannot stand for daily 12 to 16 working
  hours during that time, therefore choose resign.}
\end{itemize}
\item[Nov-2005 to Jul-2006]
\textbf{Online Gambling, Team Leader/Trader};
\href{http://www.telebizness.com/}{Telebiz Sdn Bhd}.

\begin{itemize}
\tightlist
\item
  \emph{Salary : MYR2450}
\item
  \emph{Job Task : Provides training to newbies on sportsbook trading
  purchasing stocks, need to update scores for bets financial
  settlement. Handle live-matches on corners. Sometimes need to do
  translation and also analysis job tasks.}
\item
  \emph{Resson of Leaving : Looking for better offer which introduced by
  friends.}
\end{itemize}
\end{description}

\subsubsection{Technical Experience}\label{technical-experience}

\begin{description}
\item[Jul-2015 to Present]
\href{https://github.com/Scibrokes/Betting-Strategy-and-Model-Validation}{\textbf{Betting
Strategy and Model Validation}}

\begin{itemize}
\tightlist
\item
  \emph{Learn PhantomJS for background wbdriver, markdown, setup RStudio
  server. However RSelenium and PhamtonJS faced some error and then just
  simply apply rvest to harvest the data from spbo without odds price.}
\item
  \emph{Gather and filtering the staking dataset from Sportsbook
  consultancy firm A and validate their staking models.}
\item
  \emph{Gather livescore data from}
  \href{http://www.spbo.com/eend0.htm}{\emph{spbo}} \emph{livescore
  website and filter the data.}
\item
  \emph{Natural language analysis on the scrapped livescore data to
  match the team names from firm A.}
\item
  \emph{Testing the efficiency of some coding.}
\end{itemize}
\item[Dec-2014 to Dec-2014]
\href{https://github.com/Scibrokes/Kelly-Criterion}{\textbf{Testing
Inefficiency of Sports-Bookmakers by Kelly Model}}

\begin{itemize}
\tightlist
\item
  \emph{Apply poisson model to the scrapped data from} \textbf{WebDriver
  Dynamic Webpage Scrapping} \emph{to build an prediction model.}
\item
  \emph{Rewrite the Kelly model from} \textbf{Odds Modelling and Testing
  Inefficiency of Sports-Bookmakers} \emph{in R but also optimal value}
  \(r\) \emph{which is stated in}
  \href{http://www.math.ku.dk/~rolf/teaching/thesis/DixonColes.pdf}{\emph{Dixon\&Coles1996}}
  \emph{to test the efficiency and the returns of investment based from
  the Poisson model.}
\item
  \emph{Improve the efficiency of data management and also timing of
  calculation.}
\end{itemize}
\item[Feb-2014 to Mar-2014]
\href{https://github.com/Scibrokes/Dixon-Coles1996}{\textbf{Dixon-Coles1996}}

\begin{itemize}
\tightlist
\item
  \emph{Learning} \texttt{Shiny} \emph{and} \texttt{knitr} \emph{in
  Coursera JHU} \textbf{09 Developing Data Products}, \emph{occasionally
  noticed a} \texttt{fbRanks} \emph{package, simply scrape the livescore
  of English Premier League to test the Dixon-Coles model.}
\item
  \emph{Similar with my previous research, the author wrote a scrape the
  data statical webpage but save as csv, but add-on a surface/venue
  parameter and also apply efficiency of the calculation for bigger size
  dataset. You can go to} \url{http://www.lastplanetranking.blogspot.my}
  \emph{for more details.}
\item
  \emph{I've modified a bit my model by refer the idea}
  \href{http://stackoverflow.com/questions/19532651/benchmarking-logistic-regression-using-glm-fit-bigglm-speedglm-glmnet-libli}{efficiency
  of glm packages} \emph{of the author and will review again my model
  and also write my company website}
  \href{http://www.scibrokes.com/Test/}{Scibrokes® Test Site} \emph{by
  Shiny when free.}
\item
  \emph{Additional information about the website server},
  \href{http://www.soccermetrics.net/}{SoccerMetrics},
  \href{http://www.sotdoc.co.uk/}{sotdoc} \emph{and}
  \href{http://www.matchodds.org}{matchOdds.org} \emph{might be good
  referencens for my future writing website. SotDoc roughly brief about
  the annual returns of} \href{http://www.smartodds.co.uk/}{SmartOdds}
  \emph{around 2.5\textasciitilde{}3\% while their investment returns
  rate around 7\% per annum comapre to most of sportsbookmakers 0.5\% or
  Crown 1.8\%. SoccerMetrics using Python to setup}
  \href{https://github.com/englianhu/soccermetrics-client-py}{Soccermetrics
  API Python Client} \emph{while MatchOdds apply Tomcat to manage the
  data server.}
\end{itemize}
\item[Mar-2014 to Apr-2014]
\href{https://github.com/Scibrokes/WebDriver-DynamicWebpage-Scrapping}{\textbf{WebDriver
Dynamic Webpage Scrapping}}

\begin{itemize}
\tightlist
\item
  \emph{Relenium and RSelenium published, scrape the odds price of
  sportbookmakers and also livescore data from}
  \href{http://odds.7m.hk/en/}{\emph{7M}} \emph{and}
  \href{http://info.nowgoal.com/en/}{\emph{NowGoal}} \emph{website as
  well as filter the odds price data.}
\end{itemize}
\item[Aug-2013 to Sep-2013]
\href{https://github.com/Scibrokes/Soccer-League-Web-Scraping}{\textbf{Soccer
League Web Scraping}}

\begin{itemize}
\tightlist
\item
  \emph{Learning programming to gather livescore and also odds price
  data from}
  \href{http://app.en.gooooal.com/soccer/statistic/standing.do}{\emph{Gooooal}}.
  \emph{livescore website.}
\item
  \emph{From the scrapped result, there has alot of errors and wrong
  result since the static website result unable changed once the score
  is updated. There might be some postponed matches and also suspended
  metches. Moreover dynamic webpage request selenium apps, due to Rpy
  loss maintenance and rPython,RSelenium are not yet published.
  Therefore forfeit and learn Python and started the} \textbf{WebDriver
  Dynamic Webpage Scrapping}.
\end{itemize}
\item[Apr-2008 to Apr-2010]
\href{https://www.dropbox.com/sh/ifwczokjptt6re0/AADv1VarJoQ6IgIitZBzG5c6a?dl=0}{\textbf{Odds
Modelling and Testing Inefficiency of Sports-Bookmakers}}

\begin{itemize}
\tightlist
\item
  \emph{Learn RExcel, CrystalBall, ModelRisk etc. and choose R open
  source software to start my research.}
\item
  \emph{Collect the livescore and also 1x2, Asian Handicap, Over Under
  odds price data of 29 sportsbookmakers manually from}
  \href{http://www.500wan.com}{\emph{500WAN}},
  \href{http://www.bet007.com}{\emph{BET007}} \emph{and}
  \href{http://info.nowgoal.com/en/}{\emph{NowGoal}} \emph{website and
  filter the odds price data from 2006 to 2011.}
\item
  \emph{Apply Poisson model in R to test the return of the investment.
  This research job is the most completed, success and the first
  research which write the whole odds compilation EM model and data
  management by refer to thousands of research papers in sportsbook odds
  modelling after resigned from Caspo Inc.}
\item
  \emph{Will write an proper thesis during my spared time.}
\end{itemize}
\item[Jan-2007 to Jul-2007]
\href{https://www.dropbox.com/sh/h3e6gv59onz311j/AAAFcfFOfon-kEhveTzvHGHza?dl=0}{\textbf{Apply
Poisson regression on sports odds modelling}}

\begin{itemize}
\tightlist
\item
  \emph{Write own Poisson model based on what I learnt from}
  \href{https://www.facebook.com/stuart.doyle1}{\emph{Stuart Doyle}}
  \emph{during working in Telebiz Sdn Bhd.}
\item
  \emph{Due to not master in Macro VBA, I just simply recall the concept
  which was a spreadsheet VBA Excel file from}
  \href{https://www.facebook.com/paul.judge.14}{\emph{Paul Judge}}
  \emph{for data management I accidentlly deleted few years ago.}
\item
  \emph{Remarks: Stuart and Paul used be Sportsbook consultants to
  Telebiz and setup own advisor company
  \href{http://www.sportstrust.com}{SportsTrust} during 2009/2010.}
\end{itemize}
\end{description}

\subsubsection{Time Line}\label{time-line}

\hyperdef{}{TableID3f0c1f074a8b}{\label{TableID3f0c1f074a8b}}

\hyperdef{}{MotionChartID3f0c2a216d87}{\label{MotionChartID3f0c2a216d87}}

\subsubsection{Skill}\label{skill}

\begin{longtable}[c]{@{}lr@{}}
\toprule
Skill & Level (from newbie 1 to expert 10)\tabularnewline
\midrule
\endhead
R Programming & 7\tabularnewline
MS Office & 8\tabularnewline
SQL & 3\tabularnewline
Python & 4\tabularnewline
Data Analysis & 9\tabularnewline
Customer Service & 9\tabularnewline
Sportsbook Industry & 7\tabularnewline
\bottomrule
\end{longtable}

\subsubsection{Other/Miscellaneous}\label{othermiscellaneous}

I setup \href{http://www.scibrokes.com/Test/}{Scibrokes Test Site} and
also \href{http://rstudio.scibrokes.com}{Scibrokes RStudio Server} to
manage data mining, data analysis and also calculation. You are welcome
to own yours by refer to my blog ---
\href{https://englianhu.wordpress.com/statistics/own-a-rstudio-shiny-server/}{Own
a RStudio Shiny Server}. You are welcome to contact me at
\href{mailto:englianhu@gmail.com}{\nolinkurl{englianhu@gmail.com}} for
any business coorperation since I seldom check my company mailboxes
\href{mailto:mofa@scibrokes.com}{\nolinkurl{mofa@scibrokes.com}},
\href{mailto:contact@scibrokes.com}{\nolinkurl{contact@scibrokes.com}},
\href{mailto:ryo@scibrokes.com}{\nolinkurl{ryo@scibrokes.com}}.

\subsubsection{Social Network}\label{social-network}

 \textless{}a
href=`\url{http://r.789695.n4.nabble.com/template/NamlServlet.jtp?macro=user_nodes\&user=379689}'\textgreater{}
\textless{}a
href=`\url{http://bbs.pinggu.org/home.php?mod=space\&uid=5794471}'\textgreater{}
\textless{}a
href=`\url{https://www.centos.org/forums/search.php?author_id=100465\&sr=posts}'\textgreater{}

\subsection{Appendices}\label{appendices}

\subsubsection{Documenting File
Creation}\label{documenting-file-creation}

It's useful to record some information about how your file was created.

\begin{itemize}
\tightlist
\item
  File creation date: 2015-10-17
\item
  R version 3.2.2 (2015-08-14)
\item
  R version (short form): 3.2.2
\item
  \texttt{mosaic} package version: 0.11
\item
  Additional session information
\end{itemize}

\subsubsection{References}\label{references}

\begin{itemize}
\tightlist
\item
  You are feel free to create your own CV by R Markdown V2 by refer to
  \href{http://rmarkdown.rstudio.com/developer_document_templates.html?version=0.99.484\&mode=server}{Document
  Templates}
\item
  \texttt{rticles} package version: 1.0
\item
  \href{http://rmarkdown.rstudio.com/authoring_pandoc_markdown.html}{Pandoc
  Markdown}
\item
  You can plot a
  \href{http://stackoverflow.com/questions/20695311/chronological-timeline-with-points-in-time-and-format-date}{timeline}
  graph or load the \href{http://jason.bryer.org/timeline/}{timeline}
  package.
\item
  Here I apply
  \href{https://cran.r-project.org/web/packages/googleVis/vignettes/Using_googleVis_with_knitr.html}{googleVis}
  package to plot the animated graph. You are feel free to browse over
  the
  \href{https://cran.r-project.org/web/packages/googleVis/vignettes/googleVis.pdf}{vignettes}
  for more examples.
\item
  You can also modify the layout of website by refering
  \href{http://rstudio-pubs-static.s3.amazonaws.com/27777_55697c3a476640caa0ad2099fe914ae5.html\#/}{Top
  Five CSS Customizations for R Presentations}.
\end{itemize}

\end{document}
